\bf On semidefinite-representable sets over valuation fields

### 2025-05-15 article/paper_padic_spec.tex
algo

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé la contrainte ``and
$D=0$'', car elle ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
we often refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{algorithm}
    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE A feasibility type (INFEAS, FEAS) and a solution (if FEAS)
      \vspace{0.1cm}
      \hline
      \vspace{0.1cm}
      \STATE $\mathrm{SOLVELP} (f_i,w_i,o_j)$
      \FOR{epochs = $1$ to $N$}
      \WHILE{$(j\le m)$}
      \STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
      \STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
      \STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
      \STATE compute $e=y-y^2$
      \STATE back propagate $e$ from right to left through layers
      \STATE update $w_i$
      \ENDWHILE
      \ENDFOR
    \end{algorithmic}
\end{algorithm}

>>>>

A \emph{linear programming problem} (or \emph{linear program}) \emph{with data $(A,b,c,D,e)$} is defined
as:
\begin{equation}
  \tag{LP}\label{LP}
\begin{array}{rcll}
  p^* & := & \inf_{x \in K^n} & \val \left\langle c, x \right\rangle \\
  &    & \text{s.t.}         & A x + b \geq 0\\
  & & & D x = e
\end{array}
\end{equation}
with $c \in K^n$ a fixed vector of size $n$ that represents the cost,
$A \in K^{d \times n}$, $b \in K^d$, $D \in K^{m\times n}$, $e \in K^m$ 
and $\left\langle c, x \right\rangle := c_1 x_1+\cdots +c_n x_n$.
When $A$ is a diagonal matrix\footnote{\simone{J'ai supprimé ``and
$D=0$'', car cela ne me semble pas nécessaire pour définir le ``diagonal LP''.}},
we often refer to \eqref{LP} as a \emph{diagonal} linear program.
We denote the \emph{feasible set} of \eqref{LP} by
\begin{equation*}
\begin{aligned}
  \PP  &= \{x \in K^n : Ax + b \geq 0, Dx = e\}.
\end{aligned}
\end{equation*}
A vector $x \in K^n$ is called \emph{feasible} for~\eqref{LP} if $x \in \PP$. A feasible vector $x^* \in \PP$ is called a \emph{solution} to \eqref{LP} if $p^* = \val\left\langle c,x^*\right\rangle$, namely, if the infimum in \eqref{LP} is attained at $x^*$.

@@

\begin{algorithm}
    \caption{SOLVELP($A,b,c,D,e$)}\label{algo_LP}
    \begin{algorithmic}
      \REQUIRE
      $A \in K^{d\times n}$, $b \in K^d$, $c \in K^n$, $D \in K^{m \times n}$ and $e \in K^m$
      \ENSURE [TYPE, $x$], where:
      \vspace{-0.25cm}
      \begin{itemize}
      \item[]
        TYPE $=$ INFEAS and $x=[]$ if and only if \eqref{LP} is infeasible
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ UNBOUND and $x=[]$ if and only if \eqref{LP} is feasible and unbounded
      \vspace{-0.25cm}
      \item[]
        TYPE $=$ FEAS if and only if \eqref{LP} is feasible and has a solution $x$
      \end{itemize}
      \vspace{-0.1cm}
      \hrule
      \vspace{0.1cm}
      \IF{$Dx = e$ has no solution}
      \RETURN [INFEAS, []]
      \ENDIF
      \IF{$D \neq {\bf 0}$}
      \STATE $[\mathrm{STATUS}, y] \leftarrow $
      \RETURN 
      \ENDIF
      %\FOR{epochs = $1$ to $N$}
      %\WHILE{$(j\le m)$}
      %\STATE Randomly initialize $w_i=\{w_1,w_2,\dots,w_n\}$
      %\STATE input $o_j=\{o_1,o_2,\dots,o_m\}$ in the input layer
      %\STATE forward propagate $(f_i\cdot w_i)$ through layers until getting the predicted result $y$
      %\STATE compute $e=y-y^2$
      %\STATE back propagate $e$ from right to left through layers
      %\STATE update $w_i$
      %\ENDWHILE
      %\ENDFOR
    \end{algorithmic}
\end{algorithm}
